Keep your Laziness in Check

### 2018-03-03 paper/main.tex

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
We are grateful to
%
Jos\'e Manuel Calder\'on Trilla,
Matt Parsons,
Stephanie Weirich,
Jennifer Paykin,
Robert Rand,
Antal Spector-Zabusky,
Matthew Weaver,
and the Penn PLClub
for their useful comments.
This material is based upon work supported by the
\grantsponsor{GS100000001}{National Science
  Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
No.~\grantnum{GS100000001}{1421243} ({\em Random Testing for Language
Design}), Grant No.~\grantnum{GS100000001}{1521523} ({\em Expeditions
in Computing: The Science of Deep Specification}), and \leo{Kenny,
Hengchu, ask for grant numbers names} Any opinions, findings, and
conclusions or recommendations expressed in this material are those of
the author and do not necessarily reflect the views of the National
Science Foundation.

>>>>

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
We are grateful to
%
José Manuel Calderón Trilla,
Matt Parsons,
Stephanie Weirich,
Jennifer Paykin,
Robert Rand,
Antal Spector-Zabusky,
Matthew Weaver,
and the Penn PLClub
for their useful comments.
This material is based upon work supported by the
\grantsponsor{GS100000001}{National Science
  Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
No.~\grantnum{GS100000001}{1421243} ({\em Random Testing for Language
Design}), Grant No.~\grantnum{GS100000001}{1521523} ({\em Expeditions
in Computing: The Science of Deep Specification}), and \leo{Kenny,
Hengchu, ask for grant numbers names} Any opinions, findings, and
conclusions or recommendations expressed in this material are those of
the author and do not necessarily reflect the views of the National
Science Foundation.
